Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-16 analysis/paper/paper.qmd
updated insert map size

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = 0.37, # x location of inset placement
            y = -0.23, # y location of inset placement
            width = .7, # Inset width
            height = .7, # Inset height
            scale = 0.5 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))

>>>>

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = 0.45, # x location of inset placement
            y = -0.27, # y location of inset placement
            width = .6, # Inset width
            height = .75, # Inset height
            scale = 0.5 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))
